\texttt{lightkurve}: Open source Python data analysis for NASA's Kepler, K2, and TESS missions

### 2018-02-05 paper/ms.tex
rewording

\documentclass{article}
\usepackage{amsmath, amssymb, mathtools, bm}
\usepackage{graphicx, graphics}
\usepackage{array}
\DeclareMathOperator*{\argmin}{arg\,min}

\title{PyKE: Open source Python data analysis for NASA's Kepler, K2, and TESS missions}
\author{PyKE Contributors}
\date{\today}

@@

\section{Lightcurve Basics}
    \subsection{The \texttt{LightCurve} class}
        A \texttt{LightCurve} object can be instantiated by passing a \texttt{time}
        array, a \texttt{flux} array, and optionally a \texttt{flux\_err} array which
        accounts for uncertainties in the \texttt{flux} measurements, i.e.,
        \begin{verbatim}
        from pyke.lightcurve import LightCurve
        lc = LightCurve(time, flux)
        \end{verbatim}

@@

        \begin{table}[!htb]
            \centering
            \caption{A subset of methods provided by the \texttt{LightCurve} class}
            \begin{tabular}{cp{7cm}}
                \hline
                \textbf{Method signature} & \textbf{Short description} \\
                \hline
                \texttt{stitch} & appends the attributes \texttt{flux},
                \texttt{time}, and \texttt{flux\_err} of other given
                \texttt{LighCurve} objects.\\
                \texttt{flatten} & applies a Savitzky-Golay filter to capture
                low frequency flux variations which can be then removed in order
                to aid transit detection algorithms.\\
                \texttt{fold} & folds a lightcurve at a given period and phase.\\
                \texttt{bin} &  bins a lightcurve using a block mean or median.\\
                \texttt{cdpp} &  computes the Combined Differential Photometric
                Precision (CDPP) metric, which is a proxy for the amount of
                scatter in the lightcurve signal. \\
                \texttt{plot} & displays a lightcurve.
            \end{tabular}
            \label{tab:methods}
        \end{table}

@@

        Therefore, one can, for example, perform the following series of operations
        in order to fold a lightcurve from the MAST archive
\begin{verbatim}
>>> lc_file = KeplerLightCurveFile("https://archive.stsci.edu/missions/kepler/"
... "lightcurves/0119/011904151/kplr011904151-2009350155506_llc.fits")
>>> klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=10.8234)
>>> klc.plot()
\end{verbatim}
        \begin{figure}[!htb]
            \centering
            \includegraphics[scale=.5]{figs/fold-lc.pdf}
            \caption{Folded lightcurve of target \texttt{KIC011904151} quarter 3, showing the
            transit signal of Kepler-10b.}
            \label{fig:fold-method}
        \end{figure}

@@

        For instance, the method \texttt{plot} can be used to visualize a
        given frame, which are depicted in Fig.~\ref{}
\begin{verbatim}
import numpy as np
from pyke import KeplerTargetPixelFile
tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
tpf.plot()
tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
\end{verbatim}

        \begin{figure}[!htb]
            \includegraphics[scale=.4]{figs/tpf-plot.pdf}
            \includegraphics[scale=.4]{figs/tpf-plot-aperture.pdf}
            \caption{}
            \label{fig:plot-method}
        \end{figure}

@@

Briefly, given a set of $n$ CBVs, one is interested in finding a set of $n$
coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
some cost function between the SAP flux and the set of CBVs.

@@

A runnable example of SAP flux correction for target \texttt{KOI 8462852}
can be written as follows
\begin{verbatim}
from pyke.lightcurve import KeplerCBVCorrector
cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
                         "0084/008462852/kplr008462852-2011073133259_llc.fits")
cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}

@@

PyKE contains routines to perform PSF photometry in TPFs
which are implemented in the \texttt{psf} module.

Briefly, the PSF photometry problem that PyKE solves can be formulated as
follows. Given an image $\bm{y}$, with $n$ pixels and $m$ stars, and a PSF model
$\lambda(\bm{\theta}) = \sum_{j=1}^{m} \lambda({\theta}_j)$,
find the best parameter vector
$\bm{\theta}^{*} = (\theta_1^{*}, \theta_2^{*}, ..., \theta_m^{*})$
that minimizes some cost (or loss) function $R(\lambda(\bm{\theta}), \bm{y})$
of assigning $\bm{\theta} = \bm{\theta}^{*}$.

@@

\begin{verbatim}
from pyke import KeplerTargetPixelFile
from pyke.psf import PRFPhotometry, SceneModel
from oktopus import UniformPrior

@@

\section{Acknowledgments}
PyKE is build on top of numerous packages that constitute the Python scientific
stack, more precisely, \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, and
\texttt{astropy}.

>>>>

\documentclass{article}
\usepackage{amsmath, amssymb, mathtools, bm}
\usepackage{graphicx, graphics}
\usepackage{array}
\usepackage{geometry}
\geometry{lmargin=3cm, tmargin=3cm, bmargin=2cm, rmargin=2cm}
\DeclareMathOperator*{\argmin}{arg\,min}

\title{\texttt{lightkurve}: Open source Python data analysis for NASA's Kepler, K2, and TESS missions}
\author{\texttt{lightkurve} and PyKE Contributors}
\date{\today}

@@

\section{Lightcurve Basics}
    \subsection{The \texttt{LightCurve} class}
        A \texttt{LightCurve} object can be instantiated by passing a \texttt{time}
        array, a \texttt{flux} array, and optionally a \texttt{flux\_err} array which
        accounts for uncertainties in the \texttt{flux} measurements, i.e.,
        \begin{verbatim}
        from lightkurve.lightcurve import LightCurve
        lc = LightCurve(time, flux)
        \end{verbatim}

@@

        \begin{table}[!htb]
            \centering
            \caption{A subset of methods provided by the \texttt{LightCurve} class}
            \begin{tabular}{cp{12cm}}
                \hline
                \textbf{Method signature} & \textbf{Short description} \\
                \hline
                \texttt{stitch} & appends the attributes \texttt{flux},
                \texttt{time}, and \texttt{flux\_err} of other given
                \texttt{LighCurve} objects.\\
                \texttt{flatten} & applies a Savitzky-Golay filter to capture
                low frequency flux variations which can be then removed in order
                to aid transit detection algorithms.\\
                \texttt{fold} & folds a lightcurve at a given period and phase.\\
                \texttt{bin} &  bins a lightcurve using a block mean or median.\\
                \texttt{cdpp} &  computes the Combined Differential Photometric
                Precision (CDPP) metric, which is a proxy for the amount of
                scatter in the lightcurve signal. \\
                \texttt{plot} & displays a lightcurve.
            \end{tabular}
            \label{tab:methods}
        \end{table}

@@

        Therefore, one can, for example, perform the following series of operations
        in order to fold a lightcurve from the MAST archive
\begin{verbatim}
>>> lc_file = KeplerLightCurveFile("https://archive.stsci.edu/missions/kepler/"
... "lightcurves/0119/011904151/kplr011904151-2009350155506_llc.fits")
>>> klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=0.837495)
>>> klc.plot()
\end{verbatim}
        \begin{figure}[!htb]
            \centering
            \includegraphics[scale=.5]{figs/fold-lc.pdf}
            \caption{Folded lightcurve of target \texttt{KIC011904151} quarter 3, showing the
            transit signal of Kepler-10b.}
            \label{fig:fold-method}
        \end{figure}

@@

        For instance, the method \texttt{plot} can be used to visualize a
        given frame, which are depicted in Fig.~\ref{fig:plot-method}.
\begin{verbatim}
import numpy as np
from lightkurve import KeplerTargetPixelFile
tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
tpf.plot()
tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
\end{verbatim}

        \begin{figure}[!htb]
            \includegraphics[scale=.4]{figs/tpf-plot.pdf}
            \includegraphics[scale=.4]{figs/tpf-plot-aperture.pdf}
            \caption{Displaying a given frame of a TPF using \texttt{plot}.
            Optionally, an \texttt{aperture\_mask} can be passed which is
            highlighted on the right hand side.}
            \label{fig:plot-method}
        \end{figure}

@@

Briefly, given a set of $n$ CBVs, one is interested in finding a vector of $n$
coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
some cost function between the SAP flux and the set of CBVs.

The mathematical structure of the cost function is a direct consequence of
the statistical assumptions made for data.

@@

A runnable example of SAP flux correction for target \texttt{KOI 8462852}
can be written as follows
\begin{verbatim}
from lightkurve.lightcurve import KeplerCBVCorrector
cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
                         "0084/008462852/kplr008462852-2011073133259_llc.fits")
cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}

@@

lightkurve contains routines to perform PSF photometry in TPFs
which are implemented in the \texttt{psf} module.

Briefly, the PSF photometry problem that lightkurve solves can be formulated as
follows. Given an image $\bm{y}$, with $n$ pixels and $m$ stars, and a PSF model
$\lambda(\bm{\theta}) = \sum_{j=1}^{m} \lambda({\theta}_j)$,
find the best parameter vector
$\bm{\theta}^{*} = (\theta_1^{*}, \theta_2^{*}, ..., \theta_m^{*})$
that minimizes some cost (or loss) function $R(\lambda(\bm{\theta}), \bm{y})$
of assigning $\bm{\theta} = \bm{\theta}^{*}$.

@@

\begin{verbatim}
from lightkurve import KeplerTargetPixelFile
from lightkurve.psf import PRFPhotometry, SceneModel
from oktopus import UniformPrior

@@

\section{Acknowledgments}
lightkurve is build on top of numerous packages that constitute the Scientific Python
stack, more precisely, \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, and
\texttt{astropy}.
